Colors and Residual-based Shadings in Strucplots

### 2005-09-29 trunk/vcd/inst/doc/shading.Rnw
class attributes added to grapcon functions; class of generating functions expanded; checks added to strucplot.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@465 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<shading2>>=
shade_fun <- function(res) gpar(fill = ifelse(res > 0, "lightblue", "lightsalmon"))
@

\noindent To create a mosaic display with binary shading, 
it now suffices to specify the data table along with
\codefun{shade\_fun}:

@@

<<shading3>>=
myshading_binary <- function(col = c("lightblue", "lightsalmon")) {
  if (length(col) != 2) stop("Need exactly two colors!")
  function(res) gpar(fill = ifelse(res > 0, col[1], col[2]))  
}
@

@@

<<shading4>>=
myshading_binary2 <- function(observed = NULL, residuals = NULL, expected = NULL, 
    df = NULL, col = c("lightblue", "lightsalmon")) {
  if (length(col) != 2) stop("Need exactly two colors!")
  function(res) gpar(fill = ifelse(res > 0, col[1], col[2]))  
}
class(myshading_binary2) <- "generating_function"
@

>>>>

<<shading2>>=
shade_fun <- function(res) gpar(fill = ifelse(res > 0, "lightblue", "lightsalmon"))
class(shade_fun) <- c("grapcon","shading")
@

\noindent Note the \code{class} attribute set on \codefun{shade\_fun}.
To create a mosaic display with binary shading, 
it now suffices to specify the data table along with
\codefun{shade\_fun}:

@@

<<shading3>>=
myshading_binary <- function(col = c("lightblue", "lightsalmon")) {
  if (length(col) != 2) stop("Need exactly two colors!")
  ret <- function(res) gpar(fill = ifelse(res > 0, col[1], col[2]))  
  structure(ret, class = c("grapcon","shading"))
}
@

@@

<<shading4>>=
myshading_binary2 <- function(observed = NULL, residuals = NULL, expected = NULL, 
    df = NULL, col = c("lightblue", "lightsalmon")) {
  if (length(col) != 2) stop("Need exactly two colors!")
  ret <- function(res) gpar(fill = ifelse(res > 0, col[1], col[2]))  
  structure(ret, class = c("grapcon","shading"))
}
class(myshading_binary2) <- c("grapcon_generator","shading")
@
